---
title: "hw4"
author: "cyber-atlas"
date: "March 4, 2019"
output: html_document
---

```{r}

library(ggplot2)
library(datasets)
library(dplyr)

#ChickWeight

#?ChickWeight
#head(ChickWeight)

#TODO ask and look into the data structure more

#class(ChickWeight)

#summary(ChickWeight)
```
1

```{r}
#Take the diets of the chickens 
#Count the number of rows for each diet save it
#Get the average weight for each diet save it
#Get the sd for the weigh of each diet, save it
weight0 <- ChickWeight %>%group_by(Diet) %>% filter (Time==0) %>% summarize(
    num_chicks = n(),
    avg_weight = mean(weight, na.rm=TRUE),
    sd_weight = sd(weight, na.rm = TRUE)
  ) 

#print(weight0)
weight0

```
2

```{r}

#sube]
complete <- ChickWeight %>% group_by(Chick) %>% mutate(Measurement_Count =n())

#Now make sure there are only 12 measurements
complete <- complete %>% filter(Measurement_Count == 12)

#print(complete)
head(complete, 3)

```

3

```{r}
complete <- complete %>%
  group_by(Chick) %>%
  mutate(weightgain = weight - weight[Time == 0])

head(complete, 3)

```

4

```{r}

tempDF <- complete %>% filter(Time == 21)
ggplot(tempDF, aes(x=Diet, y=weightgain))+
  geom_boxplot()

```

Diet 2 has the largest distribution of the amount of weight gained by the chickens. Diet 4 seems to have the least, with very few in the bottom IQR. Diet 3 seems to have the highest median and have the highest overall weightgain. Diet 4 can give you the best results with the least amount of risk, because the lowest weight gain was over 150. Diet 3 has a larger overall weight gain and a higher median weight gain, but there were enough chickens below 150 weighgain that they aren't outliers.

```{r}

#Used the reoder function to reorder by median
#Added expand_limits to make sure 0 is in the axis range
ggplot(tempDF, aes(x=(reorder (Diet, weightgain, FUN=median)), y=weightgain))+
  geom_boxplot()+ 
  expand_limits(y=0)

```

5

```{r}



```